\section{Project overview}

\begin{frame}{Part 1: Panels of ecological status}
  Construct complete panels of ecological status for 1990-2020 comprising every Danish waterbody.\\\bigskip
  Data generating proces:
  \begin{enumerate}
    \item Biologists' field observations with GPS coordinates.
    \item Assign point observations to matching water bodies.
    \item Impute missing observations
    \begin{itemize}
      \item Estimated by \textit{multivariate imputation by chained equations (MICE)} where a \textit{fully conditional specification (FCS)} is constituted by a conditional density for each year.
      \item Physical characteristics are included in a \textit{Bayesian ridge regression} using \textit{iteratively-reweighted regularized least-squares}.
    \end{itemize}
    \item Extrapolation of ecological status of streams for 1990 and 1991.
  \end{enumerate}
  \note{\textit{Our contributions are twofold.}\\\bigskip
    \textbf{CONTRIBUTION 1}\\
    \textbf{(...)} i.e. for all streams, lakes, fjords, coastal waters and groundwater bodies. DGP:
    \begin{enumerate}
      \item ... apply the conservative approach of using the observation that indicates the worst quality.
      \item ... included in the latest Danish waterbody plan.
      \item ... the reason is that data isn't representative but has a systematic overrepresentation of larger waterbodies and those of special concern for the ecological quality.
      \item ... by estimating a linear trend and using it to predict.
    \end{enumerate}
  }
\end{frame}
\begin{frame}{Contribution 2: Apply valuation studies}
  Shadow prices measured by the marginal current benefits of improving the quality of the Danish water environment on a national level.\\\bigskip
  I.e. the marginal willingness to pay using stated preference studies:
  \begin{itemize}
    \item \textbf{Surface waters}: Meta regressions analysis of 32 nordic studies (Zandersen et al, \textit{pending}, DCE Technical Note).
    \item \textbf{Ground water:} \textit{Choice experiment} with only 383 respondents around Limfjorden with overrepresentation of women and higher educated (Larsen et al, 2020, IFRO Working Paper).
  \end{itemize}
  \note{\textbf{CONTRIBUTION 2}\\
  }
\end{frame}