\section{Apply valuation from stated preferences}

\begin{frame}{Apply valuation from stated preferences}\label<4>{frame:Valuation}
  The marginal willingness to pay using stated preference studies:
  \begin{itemize}
    \item \textbf{Surface waters}: Meta regressions analysis of 32 nordic studies \textcolor{grey}{(Zandersen, M., S. B. Olsen, L. Martinsen, T. E. Panduro, K. H. Zemo, and B. Hasler, 2022, DCE Scientific Report no. 486)}.
    \pause
    \item \textbf{Groundwater:} Choice experiment with 383 respondents around Limfjorden \textcolor{grey}{(Larsen, T. H., T. Lundhede, and S. B. Olsen, 2020, IFRO Working Paper)}. \hspace{4.5cm}\hyperlink{app:SurveyExample}{\beamerbutton{Questionnaire Example}}
    \pause
    \begin{itemize}\normalsize
      \item Overrepresentation of women and higher educated.
      \item WTP for improvement in groundwater quality from bad to good: 4,700 DKK (2019-prices).
    \end{itemize}
    \pause
    \item \textbf{Groundwater (old):} Choice experiment with 584 respondents \textcolor{grey}{(Hasler, B., T. Lundhede, L. Martinsen, S. Neye, and J. S. Schou, 2005, NERI Technical Report no. 543)}.
    \begin{itemize}\normalsize
      \item Exclusive focus on untreated vs treated drinking water.
      \item WTP for untreated drinking water: 987 DKK (2005-prices).
    \end{itemize}      
  \end{itemize}
  \note<1>{Shadow prices express the marginal current benefits of improving the quality of the Danish water environment on a national level. Measured as \textbf{(...)}
  }
  \note<2>{We have to rely on a single Danish study concerning the value of groundwater quality.
  }
  \note<3>{They find a substantial WTP which, however, might be slightly biased by overrepresentation of groups that often show higher WTP.
  }
  \note<4>{We acknowledge that there also exists an older study with a narrow focus on drinking water which we don't use.
  }
\end{frame}