\section{Takeaways}

\begin{frame}{Main takeaways}
  \begin{enumerate}
    \item Quality of the water environment improved from 1990-2020.
    \begin{itemize}
      \item If $\Delta\text{GNNI}>\Delta\text{NNI}\Rightarrow$ GDP underestimated growth.
    \end{itemize}
    \item The marginal WTP for improvement of the water environment from \emph{bad} to \emph{good} is significant. Value of living up to the WFD:
    \begin{itemize}\normalsize
      \item DKK 17b (2020-prices) for surface waters.
      \item DKK 13b (2020-prices) for groundwater.
    \end{itemize}
    \item Sociodemographic factors affect WTP.
  \end{enumerate}
  \note{\textbf{PRELIMINARY RESULTS AND DISCUSSION}\\
    Overall, the quality of ecosystem services has improved since 1990. That is likely to be offset by the costs of GHG emissions and the depletion of exhaustable natural resources\\
    - but if it should turn out that $\Delta\text{GNNI}>\Delta\text{NNP}$,
    \begin{itemize}
      \item[$\Rightarrow$] then it would indicate that GDP growth has not been at the expense of the environment according to the definition of "strong" sustainability.\\\bigskip
    \end{itemize}
    That is, with reservations that we don't fully live up to our international commitment such as the EU Water Framework Directive and the GHG reduction path implied by the Paris Agreement DESPITE outsourcing of our most polluting factories during the period.
  }
  % \note{\textbf{ROBUSTNESS}\\
  %   To construct an unbroken time series, we need to only rely on test methods for ecological and chemical quality that has been applied since the early 90s while applying so-called "heroic assumptions", thus
  %   \begin{itemize}
  %     \item[$\Rightarrow$] \textit{Comprehensive robustness checks are necessary}
  %   \end{itemize}
  %   some of which will have to be "back-of-the-envelope" calculations.
  % }
\end{frame}