\section{Apply valuation from stated preferences}

\begin{frame}{Apply valuation from stated preferences}\label<4>{frame:Valuation}
  Marginal willingness to pay per year using stated preference studies:
  \begin{itemize}
    \item \textbf{Surface waters}: Meta regressions analysis of 32 nordic studies \textcolor{grey}{(Zandersen, M., S. B. Olsen, L. Martinsen, T. E. Panduro, K. H. Zemo, and B. Hasler, 2022, DCE Scientific Report no. 486)}.
    \pause
    \item \textbf{Groundwater:} Choice experiment with 383 respondents around Limfjorden \textcolor{grey}{(Larsen, T. H., T. Lundhede, and S. B. Olsen, 2020, IFRO Working Paper)}. \hspace{4.5cm}\hyperlink{app:SurveyExample}{\beamerbutton{Questionnaire Example}}
    \pause
    \begin{itemize}\normalsize
      \item Overrepresentation of women and higher educated.
      \item Marginal WTP per year for improvement in groundwater quality from bad to good: 4,700 DKK (2019-prices).
    \end{itemize}
    \pause
    \item \textbf{Groundwater (old):} Choice experiment with 584 respondents \textcolor{grey}{(Hasler, B., T. Lundhede, L. Martinsen, S. Neye, and J. S. Schou, 2005, NERI Technical Report no. 543)}.
    \begin{itemize}\normalsize
      \item Exclusive focus on untreated vs treated drinking water.
      \item WTP for untreated drinking water: 987 DKK (2005-prices).
    \end{itemize}      
  \end{itemize}
  \note<1>{Shadow prices express the marginal current benefits of improving the quality of the Danish water environment on a national level. Measured as \textbf{(...)}
  \begin{itemize}
    \item \textbf{(...)} comprising 124 estimates of marginal WTP for improvements in water quality.
  \end{itemize}
  }
  \note<2>{We have to rely on a single Danish study concerning the value of groundwater quality.
  }
  \note<3>{They find a substantial WTP which, however, might be slightly biased by overrepresentation of groups that often show higher WTP.
  }
  \note<4>{We acknowledge that there also exists an older study with a narrow focus on drinking water which we don't use.
  }
\end{frame}

\begin{frame}{Benefit transfer for surface water}
  \only<1>{
    Meta analysis function for benefit transfer of the marginal WTP per year for average water quality of the waterbodies of category $j$ (streams, lakes, or coastal waters) in catchment area $v$ in year $t$:
    \begin{align*}
      \ln \mu_{u,v,t}^{w,j}=&\beta_0+.55\overline{\ln Q}_{j,v,t}-.38D_{j}^{lake}-.01SL_{j,v}+.12\ln PSL_{j,v}-.07\ln PAL_v\\
      &+1.45\ln y_{v,t}+.5D_{v,t}^{age},\quad\overline{\ln Q}_{j,v,t}=\frac{1}{\mathcal{I}_{j,v}}\sum_i^{\mathcal{I}_{j,v}}\mathbb{1}_{\mathbb{N}^+}(Q_{i,j,v,t})\ln Q_{i,j,v,t}
    \end{align*}
    \begin{itemize}
      \item[$\overline{Q}_{jvt}$] mean water quality of category $j$ in $v$ at year $t$ (deviation from “Bad”)
      \item[$D_{j}^{lake}$] dummy for category $j$ being lakes
      \item[$SL_{jv}$] shore length of category $j$ (in 1,000 km) in catchment area $v$
      \item[$PSL_{jv}$] shore length of category $j$ relative to total shore length in area $v$
      \item[$PAL_{v}$] proportion of agricultural land in catchment area $v$
      \item[$y_{vt}$] average household income in catchment area $v$ at year $t$
      \item[$D_{vt}^{age}$] dummy for mean age of inhabitants $\geq$ 45 years in $v$ at year $t$
    \end{itemize}
  }
  % \only<2>{
  %   Meta analysis function for benefit transfer of the marginal WTP per year for average water quality of the $\mathcal{I}$ waterbodies of category $j$ (streams, lakes, or coastal waters) in catchment area $v$ in year $t$:
  %   \begin{align*}
  %     \ln \mu_{u,v,t}^{w,j}=&\beta_0+.55\frac{1}{\mathcal{I}_{j,v}}\sum_i^{\mathcal{I}_{j,v}}\mathbb{1}_{\mathbb{N}^+}(Q_{i,j,v,t})\ln Q_{i,j,v,t}-.38D_{j}^{lake}-.01SL_{j,v}\\
  %       &+.12\ln PSL_{j,v}-.07\ln PAL_v+1.45\ln y_{v,t}+.5D_{v,t}^{age}
  %   \end{align*}
  %   \begin{itemize}
  %     \item[$Q_{i,j,v,t}$] quality of waterbody $i$ of category $j$ in $v$ (deviation from “Bad”)
  %     \item[$D_{j}^{lake}$] dummy for category $j$ being lakes
  %     \item[$SL_{j,v}$] shore length of category $j$ in catchment area $q$ (in 1,000 km)
  %     \item[$PSL_{j,v}$] shore length of category $j$ relative to total shore length in $q$
  %     \item[$PAL_{v}$] proportion of agricultural land in catchment area $q$
  %     \item[$\ln y_{v,t}$] average household income in catchment area $q$
  %     \item[$D_{v,t}^{age}$] dummy for mean age of inhabitants in q $\geq$ 45 years
  %   \end{itemize}
  % }
\end{frame}

\begin{frame}{Shadow value of groundwater}
  Use value of (clean) groundwater per household in catchment area $v$ for year $t$:
  \begin{align*}
    \mu_{u,v,t}^{w,gw}=WTP_{t}^{gw}\frac{b_{v,t}^{good}}{B_{v,t}},\quad\quad WTP_{t}^{gw}=\frac{WTP_{2020}^{gw}}{\prod_{k=1}^{2020-t}(1+\eta g_{2020-k})}
  \end{align*}
  \begin{itemize}
    \item[{\scriptsize$WTP_{t}^{gw}$}] marginal WTP per household for “Good” groundwater quality
    \item[$b_{v,t}^{good}$] number of wells with “Good” groundwater quality
    \item[$B_{v,t}$] total number of well in catchment area $v$
    \item[$\eta$] \inline{income elasticity = 1 or 1.45 as for surface waters?}
    \item[$g_{t}$] national average growth rate of household income over the last three years.
  \end{itemize}
\end{frame}